---
title: "Scottish Health Survey Gambling Data"
author: "Scott Kilgariff"
date: "08/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Data extracted from <a href = "https://www.gov.scot/collections/scottish-health-survey/", target = "_blank"> Scottish Health Survey </a> (SHS) covering the period from 2012 to 2017.

Data for 2021 is expected to be made available in November 2022. Questions on gambling were not included in the SHS during the years 2018 to 2020.

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(readxl)
library(httr)
library(janitor)
library(ggplot2)
```

## Percentage of respondents answering "Yes" to spending money on the following, split by age group

```{r grid_1, out.width = "100%", echo=FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=3, ,results="asis"}

df_data <- read_csv("df_sheet.csv")

df_plot <- df_data %>% 
  filter(response == "Yes" & 
           description =="age_grp")

df_plot$measure_map <- gsub('Spent any money on:', '', df_plot$measure_map)

measures <- unique(df_plot$measure_map)

library(viridis)

plot_sets <- c(1,2,3,4,5)

for (i in seq_along(measures)){
  
  cat("  \n###",  measures[i], "  \n")
  
  df_plot_slice <- df_plot %>% filter(measure_map == measures[i])
  c_scale_start <- min(df_plot_slice$value)/100
  c_scale_end <- max(df_plot_slice$value)/100
  
  p <- ggplot(df_plot_slice, aes(year, category, fill=value)) +
    geom_raster() +
    scale_y_discrete(limits=rev, labels= c("75+", "65 to 74","55 to 64","45 to 54","35 to 44","25 to 34","16 to 24")) +
    scale_fill_viridis(direction = -1, option = "B", begin = 0.25, end = 0.75, alpha = 0.5) +
    geom_hline(yintercept=c(1.5,2.5,3.5,4.5,5.5,6.5,7.5)) +
    geom_text(aes(label = round(value, 1))) +
    ylab("Age groups") +
    theme_classic() + 
    facet_wrap(~ sex, labeller = label_wrap_gen(), ncol=3) +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      strip.background = element_blank(),
      panel.border = element_rect(colour = NA, fill = NA),
      strip.text = element_text(size = 15),
      axis.text = element_text(size = 12))
  
  print(p)
  cat("  \n")
}

```

## Percentage of respondents answering "Yes" to spending money on the following, split by deprivation quintile

```{r grid_2, out.width = "100%", echo=FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=3, ,results="asis"}

df_plot <- df_data %>% 
  filter(response == "Yes" & 
           description =="simd_quintiles")

df_plot$measure_map <- gsub('Spent any money on:', '', df_plot$measure_map)

df_plot$category <- ordered(df_plot$category, levels = c("least_deprived", "x2", "x3", "x4", "most_deprived"))

measures <- unique(df_plot$measure_map)

library(viridis)

plot_sets <- c(1,2,3,4,5)

for (i in seq_along(measures)){
  
  cat("  \n###",  measures[i], "  \n")
  
  df_plot_slice <- df_plot %>% filter(measure_map == measures[i])
  c_scale_start <- min(df_plot_slice$value)/100
  c_scale_end <- max(df_plot_slice$value)/100
  
  p <- ggplot(df_plot_slice, aes(year, category, fill=value)) +
    geom_raster() +
    scale_fill_viridis(direction = -1, option = "B", begin = 0.25, end = 0.75, alpha = 0.5) +
    geom_hline(yintercept=c(1.5,2.5,3.5,4.5,5.5,6.5,7.5)) +
    geom_text(aes(label = round(value, 1))) +
    ylab("Age groups") +
    theme_classic() + 
    facet_wrap(~ sex, labeller = label_wrap_gen(), ncol=3) +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      strip.background = element_blank(),
      panel.border = element_rect(colour = NA, fill = NA),
      strip.text = element_text(size = 15),
      axis.text = element_text(size = 12))
  
  print(p)
  cat("  \n")
}

```

## Percentage of respondents answering "Yes" to spending money on the following, split by income

```{r grid_3, out.width = "100%", echo=FALSE, message=FALSE, warning=FALSE, fig.width=10,fig.height=3, ,results="asis"}

df_plot <- df_data %>% 
  filter(response == "Yes" & 
           description =="equivalised_income")

df_plot$measure_map <- gsub('Spent any money on:', '', df_plot$measure_map)

measures <- unique(df_plot$measure_map)

library(viridis)

plot_sets <- c(1,2,3,4,5)

for (i in seq_along(measures)){
  
  cat("  \n###",  measures[i], "  \n")
  
  df_plot_slice <- df_plot %>% filter(measure_map == measures[i])
  c_scale_start <- min(df_plot_slice$value)/100
  c_scale_end <- max(df_plot_slice$value)/100
  
  p <- ggplot(df_plot_slice, aes(year, category, fill=value)) +
    geom_raster() +
    scale_fill_viridis(direction = -1, option = "B", begin = 0.25, end = 0.75, alpha = 0.5) +
    geom_hline(yintercept=c(1.5,2.5,3.5,4.5,5.5,6.5,7.5)) +
    geom_text(aes(label = round(value, 1))) +
    ylab("Age groups") +
    theme_classic() + 
    facet_wrap(~ sex, labeller = label_wrap_gen(), ncol=3) +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      strip.background = element_blank(),
      panel.border = element_rect(colour = NA, fill = NA),
      strip.text = element_text(size = 15),
      axis.text = element_text(size = 12))
  
  print(p)
  cat("  \n")
}

```

